\section{Publications}
\begin{bibsectionfirst}

\item Owen S. Hofmann, Sangman Kim, Alan M. Dunn, Michael Z. Lee, Emmett
Witchel.
Inktag: Secure Applications on an Untrusted Operating System.
To appear in \emph {Proceedings of the 18th International Conference on
Architectural Support for Programming Languages and Operating Systems
(ASPLOS), Houston, TX, March 2013}

\end{bibsectionfirst}
\begin{bibsection}

\item Edmund B. Nightingale, Jeremy Elson, Jinliang Fan, Owen Hofmann, Jon
Howell, and Yutaka Suzue.
Flat Datacenter Storage. 
In \emph{Proceedings of the 10th USENIX Symposium on Operating Systems
Design and Implementation (OSDI), Hollywood, CA, October 2012}

\item Owen S. Hofmann, Alan Dunn, Sangman Kim, Indrajit Roy, Emmett Witchel.
Ensuring Operating System Kernel Integrity with OSck.
In \emph{Proceedings of the 16th International Conference on Architectural
Support for Programming Languages and Operating Systems (ASPLOS), Newport
Beach, CA, March 2011} 

\item Sangman Kim, Michael Z. Lee, Alan M. Dunn, Owen S. Hofmann, Xuan
Wang, Emmett Witchel, Donald E. Porter.
Improving Server Applications with System Transactions.
In \emph{Proceedings of the 7th ACM European Conference on Computer Systems
(EuroSys), Bern, Switzerland, April 2012}

\item Alan M. Dunn, Owen S. Hofmann, Brent Waters, Emmett Witchel.
Cloaking Malware with the Trusted Platform Module.
In \emph{Proceedings of the 20th USENIX Security Symposium, San Francisco,
CA, August 2011}

\item Scott Wolchok, Owen S. Hofmann,  Nadia Heninger,  Edward W. Felten,
J. Alex Halderman, Christopher J. Rossbach, Brent Waters, Emmett Witchel.
Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs.
 In \emph{Proceedings of the 17th Network and Distributed System Security
Symposium (NDSS), San Diego, California, February, 2010}


\item Christopher J. Rossbach, Owen S. Hofmann, Emmett Witchel.
Is Transactional Memory Programming Actually Easier?
In \emph{Proceedings of the  15th ACM SIGPLAN Annual Symposium on
Principles and Practice of Parallel Programming (PPoPP), Bangalore, India,
January 2010} 
 
\item Donald E. Porter, Owen S. Hofmann, Christopher J. Rossbach, Alexander
Benn, Emmett Witchel.
Operating System Transactions.
In \emph{Proceedings of the 22nd ACM Symposium on Operating Systems
Principles (SOSP), Big Sky, MT, October 2009} 
 
\item Christopher J. Rossbach, Owen S. Hofmann, Emmett Witchel.
Is Transactional Memory Programming Actually Easier?
In \emph{Proceedings of the  8th Annual Workshop on Duplicating,
Deconstructing, and Debunking (WDDD), Austin, Texas June 2009} 
 
\item Owen S. Hofmann, Christopher J. Rossbach, Emmett Witchel.
Maximum Benefit from a Minimal HTM.
In \emph{Proceedings of the 14th International Conference on Architectural
Support for Programming Languages and Operating Systems (ASPLOS),
Washington DC, March 2009} 
 
\item Christopher J. Rossbach, Owen S. Hofmann, Donald E. Porter, Hany E.
Ramadan, Aditya Bhandari, Emmett Witchel.
TxLinux/MetaTM: Transactional Memory and the Operating System.
In \emph{Communications of the ACM, September 2008} 
 
\item Hany E. Ramadan, Christopher J. Rossbach, Donald E. Porter, Owen S.
Hofmann, Aditya Bhandari, Emmett Witchel.
MetaTM/TxLinux: Transactional Memory For An Operating System.
 In \emph{IEEE Micro, Jan/Feb 2008}
 
\item Christopher J. Rossbach, Owen S. Hofmann, Donald E. Porter, Hany E.
Ramadan, Aditya Bhandari, Emmett Witchel.
TxLinux: Using and Managing Hardware Transactional Memory in an
Operating System.
In \emph{Proceedings of the 21st ACM Symposium on Operating Systems
Principles (SOSP), Stevenson, WA October 2007} 
 
\item Owen S. Hofmann, Donald E. Porter, Hany E. Ramadan, Christopher J.
Rossbach, Emmett Witchel.
Solving Difficult HTM Problems Without Difficult Hardware.
In \emph{Proceedings of the 2nd Workshop on Transactional Computing
(TRANSACT), Portland, OR August 2007.} 
 
\item Hany E. Ramadan, Christopher J. Rossbach, Donald E. Porter, Owen S.
Hofmann, Aditya Bhandari, Emmett Witchel.
MetaTM/TxLinux: Transactional Memory For An Operating System.
In \emph{Proceedings of the International Symposium on Computer
Architecture 2007 (ISCA), San Diego, CA June 2007.} 
 
\item Donald E. Porter, Owen S. Hofmann, Emmett Witchel.
Is the Optimism in Optimistic Concurrency Warranted? 
In \emph{Proceedings of the 11th Workshop on Hot Topics in Operating
Systems (HotOS) San Diego, CA May 2007.} 
 
\item Sasha Ames, Nikhil Bobb, Kevin Greenan, Owen Hofmann, Mark W. Storer,
Carlos Maltzahn, Ethan L. Miller, Scott A. Brandt.
LiFS: An Attribute-Rich File System for Storage Class Memories.
In \emph{Proceedings of the 23rd IEEE / 14th NASA Goddard Conference on
Mass Storage Systems and Technologies (MSST), College Park, MD May
2006.} 
\end{bibsection}

