%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist}
\newenvironment{bibsectionfirst}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% 

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{comment}

\begin{document}
\makeheading{Owen S.~Hofmann}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{http://www.cs.utexas.edu/}{Department of Computer Science} &
   \textit{Phone:} (512) 576-2109 \\
\href{http://www.utexas.edu/}{The University of Texas at Austin} &
   \textit{E-mail:} \href{mailto:osh@cs.utexas.edu}{osh@cs.utexas.edu} \\
1616 Guadalupe, Suite 2.408 & \textit{Web:}
   \href{http://www.cs.utexas.edu/~osh/}{www.cs.utexas.edu/{\footnotesize$\sim$}osh/} \\
Austin, TX 78701 & \\
\end{tabular}

\section{Research Interests}
%
Operating systems, architecture, parallel programming

\section{Education}
%
\href{http://www.utexas.edu/}{\textbf{The University of Texas at Austin}},
Austin, Texas
\begin{outerlist}

\item[] Ph.D., Computer Science, expected 2013
        \begin{innerlist}
        \item Adviser:
              \href{http://www.cs.utexas.edu/~witchel/}
                   {Emmett Witchel}
        \item Thesis: Rethinking Operating System Trust
        \end{innerlist}

\end{outerlist}

\bigskip

\href{http://www.amherst.edu}{\textbf{Amherst College}}, Amherst,
Massachusetts
\begin{outerlist}
\item[] B.A. \emph{Magna cum Laude}, Computer Science, May 2006
        \begin{innerlist}
        \item Thesis: \emph{Reference Trace Reduction via Recency
Distribution Sampling}
        \end{innerlist}

\end{outerlist}

\section{Publications}
\begin{bibsectionfirst}

\item Owen S. Hofmann, Sangman Kim, Alan M. Dunn, Michael Z. Lee, Emmett
Witchel.
Inktag: Secure Applications on an Untrusted Operating System.
To appear in \emph {Proceedings of the 18th International Conference on
Architectural Support for Programming Languages and Operating Systems
(ASPLOS), Houston, TX, March 2013}

\end{bibsectionfirst}
\begin{bibsection}

\item Edmund B. Nightingale, Jeremy Elson, Jinliang Fan, Owen Hofmann, Jon
Howell, and Yutaka Suzue.
Flat Datacenter Storage. 
In \emph{Proceedings of the 10th USENIX Symposium on Operating Systems
Design and Implementation (OSDI), Hollywood, CA, October 2012}

\item Owen S. Hofmann, Alan Dunn, Sangman Kim, Indrajit Roy, Emmett Witchel.
Ensuring Operating System Kernel Integrity with OSck.
In \emph{Proceedings of the 16th International Conference on Architectural
Support for Programming Languages and Operating Systems (ASPLOS), Newport
Beach, CA, March 2011} 

\item Sangman Kim, Michael Z. Lee, Alan M. Dunn, Owen S. Hofmann, Xuan
Wang, Emmett Witchel, Donald E. Porter.
Improving Server Applications with System Transactions.
In \emph{Proceedings of the 7th ACM European Conference on Computer Systems
(EuroSys), Bern, Switzerland, April 2012}

\item Alan M. Dunn, Owen S. Hofmann, Brent Waters, Emmett Witchel.
Cloaking Malware with the Trusted Platform Module.
In \emph{Proceedings of the 20th USENIX Security Symposium, San Francisco,
CA, August 2011}

\item Scott Wolchok, Owen S. Hofmann,  Nadia Heninger,  Edward W. Felten,
J. Alex Halderman, Christopher J. Rossbach, Brent Waters, Emmett Witchel.
Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs.
 In \emph{Proceedings of the 17th Network and Distributed System Security
Symposium (NDSS), San Diego, California, February, 2010}


\item Christopher J. Rossbach, Owen S. Hofmann, Emmett Witchel.
Is Transactional Memory Programming Actually Easier?
In \emph{Proceedings of the  15th ACM SIGPLAN Annual Symposium on
Principles and Practice of Parallel Programming (PPoPP), Bangalore, India,
January 2010} 
 
\item Donald E. Porter, Owen S. Hofmann, Christopher J. Rossbach, Alexander
Benn, Emmett Witchel.
Operating System Transactions.
In \emph{Proceedings of the 22nd ACM Symposium on Operating Systems
Principles (SOSP), Big Sky, MT, October 2009} 
 
\item Christopher J. Rossbach, Owen S. Hofmann, Emmett Witchel.
Is Transactional Memory Programming Actually Easier?
In \emph{Proceedings of the  8th Annual Workshop on Duplicating,
Deconstructing, and Debunking (WDDD), Austin, Texas June 2009} 
 
\item Owen S. Hofmann, Christopher J. Rossbach, Emmett Witchel.
Maximum Benefit from a Minimal HTM.
In \emph{Proceedings of the 14th International Conference on Architectural
Support for Programming Languages and Operating Systems (ASPLOS),
Washington DC, March 2009} 
 
\item Christopher J. Rossbach, Owen S. Hofmann, Donald E. Porter, Hany E.
Ramadan, Aditya Bhandari, Emmett Witchel.
TxLinux/MetaTM: Transactional Memory and the Operating System.
In \emph{Communications of the ACM, September 2008} 
 
\item Hany E. Ramadan, Christopher J. Rossbach, Donald E. Porter, Owen S.
Hofmann, Aditya Bhandari, Emmett Witchel.
MetaTM/TxLinux: Transactional Memory For An Operating System.
 In \emph{IEEE Micro, Jan/Feb 2008}
 
\item Christopher J. Rossbach, Owen S. Hofmann, Donald E. Porter, Hany E.
Ramadan, Aditya Bhandari, Emmett Witchel.
TxLinux: Using and Managing Hardware Transactional Memory in an
Operating System.
In \emph{Proceedings of the 21st ACM Symposium on Operating Systems
Principles (SOSP), Stevenson, WA October 2007} 
 
\item Owen S. Hofmann, Donald E. Porter, Hany E. Ramadan, Christopher J.
Rossbach, Emmett Witchel.
Solving Difficult HTM Problems Without Difficult Hardware.
In \emph{Proceedings of the 2nd Workshop on Transactional Computing
(TRANSACT), Portland, OR August 2007.} 
 
\item Hany E. Ramadan, Christopher J. Rossbach, Donald E. Porter, Owen S.
Hofmann, Aditya Bhandari, Emmett Witchel.
MetaTM/TxLinux: Transactional Memory For An Operating System.
In \emph{Proceedings of the International Symposium on Computer
Architecture 2007 (ISCA), San Diego, CA June 2007.} 
 
\item Donald E. Porter, Owen S. Hofmann, Emmett Witchel.
Is the Optimism in Optimistic Concurrency Warranted? 
In \emph{Proceedings of the 11th Workshop on Hot Topics in Operating
Systems (HotOS) San Diego, CA May 2007.} 
 
\item Sasha Ames, Nikhil Bobb, Kevin Greenan, Owen Hofmann, Mark W. Storer,
Carlos Maltzahn, Ethan L. Miller, Scott A. Brandt.
LiFS: An Attribute-Rich File System for Storage Class Memories.
In \emph{Proceedings of the 23rd IEEE / 14th NASA Goddard Conference on
Mass Storage Systems and Technologies (MSST), College Park, MD May
2006.} 
\end{bibsection}



\section{Awards}
%
CACM Invited Article for September 2008: \\
Christopher J. Rossbach,
Owen S. Hofmann, Donald E. Porter, Hany E. Ramadan, Aditya Bhandari,
Emmett Witchel. TxLinux: Using and Managing Transactional Memory in
an Operating System

\bigskip

IEEE Top Pick for 2008: \\
Hany E. Ramadan, Christopher J. Rossbach, Donald E. Porter,
Owen S. Hofmann, Aditya Bhandari, Emmett Witchel.
MetaTM/TxLinux: Transactional Memory for an Operating System

\bigskip

SOSP 2007 Audience Choice Best Paper: \\
Christopher J. Rossbach,
Owen S. Hofmann, Donald E. Porter, Hany E. Ramadan, Aditya Bhandari,
Emmett Witchel. 
TxLinux: Managing and Supporting Hardware Transactional Memory in an
Operating
System

\bigskip

Microelectronics and Computer Development (MCD) Graduate Fellowship,
The University of Texas at Austin, August 2006 to May 2007

%\pagebreak

\section{Experience}
\href{http://www.cs.utexas.edu}{\textbf{The University of Texas at Austin,
Department of Computer Science}}
\begin{outerlist}

\item[] \textit{Research Assistant}%
    \hfill \textbf{May 2007 to present}
    \begin{innerlist}
        \item TxLinux 2.6 
        \begin{innerlist}
           \item Worked on team to develop TxLinux, the first operating system
to use hardware transactional memory for synchronization
           \item Designed and implemented \emph{cooperative transactional
spinlocks}, forming the basis for large-scale automatic conversion of the
Linux kernel to use hardware transactions
           \item Published in ISCA '07 and SOSP '07
        \end{innerlist}
        \item TxLinux 2.4
        \begin{innerlist}
           \item Applied techniques from TxLinux 2.6 to Linux 2.4 to
demonstrate the benefit of hardware transactional memory for
improving coarse-grained synchronization performance in the operating
system
           \item Introduced \emph{transaction ordering}, a novel technique for
unifying hardware and software transactional memory in user applications
           \item Published in ASPLOS '09
        \end{innerlist}
        \item TxOS
        \begin{innerlist}
           \item Worked on team to develop TxOS, a version of Linux
providing \emph{system transactions} to ensure atomic, isolated and
consistent updates to diverse system resources
           \item Modified the ext3 file system to provide durable
transactional updates
           \item Published in SOSP '09
        \end{innerlist}
        \item Unvanish
        \begin{innerlist}
           \item Identified vulnerabilities in the Vanish system for
self-destructing data
           \item Designed and implemented Unvanish, a system to recover
data protected by Vanish
           \item Published in NDSS '10
         \end{innerlist}
         \item OSck
         \begin{innerlist}
            \item Designed and implemented a system for efficient
hypervisor-based kernel rootkit detection based on the Linux KVM hypervisor
            \item Published in ASPLOS '11
         \end{innerlist}
         \item InkTag
         \begin{innerlist}
            \item Designed and implemented InkTag, a system for securely
executing applications under an untrusted operating system
            \item To appear in ASPLOS '13
         \end{innerlist}
    \end{innerlist}
\item[] \textit{Assistant Instructor}%
        \hfill \textbf{January 2012 to May 2012}
        \begin{innerlist}
           \item CS429: Computer Organization and Architecture
           \begin{innerlist}
              \item Served as instructor for an introductory undergraduate
computer architecture course (77 students)
              \item Developed new lectures and exams
           \end{innerlist}
        \end{innerlist}
\item[] \textit{Teaching Assistant}%
        \hfill \textbf{August 2007 to December 2007}
        \begin{innerlist}
           \item CS372H: Operating Systems Honors
           \begin{innerlist}
              \item Held office hours, graded undergraduate lab assignments and exams
              \item Developed new lab assignments on synchronization
              \item Designed a user study based on student experience and
performance with synchronization labs
              \item Study results later published in PPoPP '10
           \end{innerlist}
        \end{innerlist}
\end{outerlist}

\bigskip

\href{http://research.microsoft.com}{\textbf{Microsoft Research}}
\begin{outerlist}

\item[] \textit{Intern}
    \hfill \textbf{June 2010 to August 2010}
    \begin{innerlist}
        \item Flat Datacenter Storage
        \begin{innerlist}
           \item Worked on team developing initial implementation of Flat
Datacenter Storage (FDS)
           \item Built initial implementation of failure recovery within
FDS
           \item FDS currently holds records in both ``Indy'' and
``Daytona'' categories for the MinuteSort benchmark
(\href{http://www.sortbenchmark.org}{www.sortbenchmark.org}).
           \item Published in OSDI '12
        \end{innerlist}
     \end{innerlist}
\end{outerlist}

\begin{comment}

\section{Technical\\Skills}
C, C++, x86 assembly, Java, Python, PHP

\bigskip

Kernel hacking, parallel programming

\bigskip

Data analysis and graphing with the R
software environment for statistical computing

\section{References}
\end{comment}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
